Behavior Driven Development in Haskell

### 2012-05-24 paper.tex
Add code examples for "integrating multiple test suites"

\usepackage{amsmath}

@@

\begin{quote}
\small
\begin{verbatim}
spec :: Specs
spec = do
  describe "reverse" $ do
    it "reverses a list" $
      reverse [1 :: Int, 2, 3] @?= [3, 2, 1]

@@

TBD(@sol): talk about Cabal.

\begin{quote}
\small
\begin{verbatim}
TBD: Example
Test-Suite spec
  Main-Is: Spec.hs
  Type: exitcode-stdio-1.0
  ...

Test-Suite doctests
  Main-Is: doctests.hs
  Type: exitcode-stdio-1.0
  ...
\end{verbatim}
\end{quote}

\begin{quote}
\small
\begin{verbatim}
TBD: Spec.hs comes here
\end{verbatim}
\end{quote}

\begin{quote}
\small
\begin{verbatim}
TBD: doctest.hs comes here
\end{verbatim}
\end{quote}

>>>>

\usepackage{amsmath}
\usepackage{url}

@@

\begin{quote}
\small
\begin{verbatim}
import Test.Hspec.Monadic
spec :: Specs
spec = do
  describe "reverse" $ do
    it "reverses a list" $
      reverse [1 :: Int, 2, 3] @?= [3, 2, 1]

@@

\begin{itemize}

\item @kazu: Can you add a reference to:
\url{http://www.haskell.org/cabal/users-guide/developing-packages.html#test-suites}
\item @kazu: should this subsection go into "best current practice"?

\item It is important that testing is automated, including running of test
    suites.  Where should we put this?
\end{itemize}

\noindent Cabals test feature can be used to automatically run tests.  A cabal
file can contain multiple test suites, so it is possible to define test suites
for Doctest and \hspec{} in a single cabal file.

A driver for Hspec looks like so:

\begin{quote}
\small
\begin{verbatim}
-- file Spec.hs
import Test.Hspec.Monadic
main = hspecX spec
\end{verbatim}
\end{quote}

\noindent And a corresponding Cabal test suite section like so:

\begin{quote}
\small
\begin{verbatim}
test-suite spec
  type:          exitcode-stdio-1.0
  main-is:       Spec.hs
  build-depends: base, hspec
\end{verbatim}
\end{quote}

\noindent A driver for Doctest looks like so:

\begin{quote}
\small
\begin{verbatim}
-- file doctests.hs
import Test.DocTest
main = doctest ["src/Main.hs"]
\end{verbatim}
\end{quote}

\noindent And a corresponding Cabal test suite section like so:

\begin{quote}
\small
\begin{verbatim}
test-suite doctests
  type:          exitcode-stdio-1.0
  main-is:       doctests.hs
  build-depends: base, doctest
\end{verbatim}
\end{quote}
